\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small\textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Prem Kumar G} \\ \vspace{1pt}
    \small Bengaluru, India $|$
    \href{mailto:premkumarmvks@gmail.com}{\underline{premkumarmvks@gmail.com}} $|$
    +91-9538507538 \\
    \href{https://linkedin.com/in/premgowda98}{\underline{linkedin.com/in/premgowda98}} $|$
    \href{https://github.com/premgowda98}{\underline{github.com/premgowda98}} $|$
    \href{https://portfolio.premgowda.in}{\underline{portfolio.premgowda.in}}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\small{Software Development Engineer with 4+ years building high-scale distributed systems for Fortune 500 retail and fintech platforms. Specialized in event-driven architectures processing millions of daily events using Golang, Kafka, and Kubernetes. Proven track record improving data accuracy from 90\% to 99\%, reducing infrastructure overhead by 40\%, and leading cross-functional initiatives. Experienced in backend development, platform engineering, and building resilient microservices at scale.}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Core Expertise}{: Golang, Python, Kubernetes, Docker, Microservices Architecture} \\
     \textbf{Backend \& Messaging}{: Kafka (Avro/CDC), RabbitMQ, Redis, PostgreSQL, RESTful APIs} \\
     \textbf{Cloud \& Infrastructure}{: Azure, Harness CI/CD, GitHub Actions} \\
     \textbf{Data Engineering}{: Databricks, Apache Spark, PySpark, Spark SQL, Delta Lake, Apache Avro} \\
     \textbf{Observability}{: Grafana, Prometheus, OpenTelemetry, Dynatrace} \\
     \textbf{AI \& Automation}{: LLMs, RAG (Langchain, LlamaIndex), Gemini AI, n8n}
    }}
 \end{itemize}

%-----------PROFESSIONAL EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {ZopSmart (Kroger.com)}{Bengaluru, India}
      {Software Development Engineer 2 (SDE-2)}{December 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Identified and resolved critical data integrity issues in Kafka event publishing pipelines processing 1-3 million daily events (20M+ during full loads) by implementing proper Avro schema encoding and validation; drove schema standardization across 5+ internal teams and consumer services to ensure data consistency.}
        \resumeItem{Co-designed Generic Event Schema with Avro nested metadata and schema registry pattern; reduced downstream processing overhead by 40\% while maintaining 100\% backward compatibility across multiple consumer services, eliminating workflow restarts.}
        \resumeItem{Drove 4-month cross-functional data quality initiative spanning 3 teams; delivered internal reconciliation tooling to analyze and classify mismatched records, increasing data accuracy from 90-95\% to 99\% and preventing downstream calculation errors.}
        \resumeItem{Designed and implemented Harness CI/CD pipeline for feature environment deployments across 5-6 microservices, enabling isolated testing before production; reduced environment-related bug escapes by 30\% and cut developer feedback cycles from hours to minutes.}
        \resumeItem{Mentored 2 junior engineers through design RFCs, code reviews, and knowledge-sharing sessions on Kubernetes orchestration, Kafka streaming patterns, and Golang best practices.}
      \resumeItemListEnd

    \resumeSubheading
      {Edgebricks}{Bengaluru, India}
      {Backend Engineer}{September 2024 -- November 2024}
      \resumeItemListStart
        \resumeItem{\textit{Note: Early-stage AI startup that ceased operations due to funding challenges. Delivered complete MVP within 3-month timeframe.}}
        \resumeItem{Built production-ready RAG-based LLM chatbot using Langchain and LlamaIndex, enabling natural language querying over business data and delivering actionable insights with high user adoption across pilot clients.}
        \resumeItem{Transformed monolithic chatbot application into multi-tenant SaaS platform using Docker and Ansible automation, supporting concurrent clients with fully isolated data environments and tenant-specific configurations.}
        \resumeItem{Designed and implemented RESTful APIs with rate limiting, authentication middleware, and Redis-based caching to optimize API response times and throughput for production workloads.}
      \resumeItemListEnd

    \resumeSubheading
      {Insight Consultants}{Bengaluru, India}
      {Python Developer}{March 2022 -- September 2024}
      \resumeItemListStart
        \resumeItem{Designed and built loan underwriting automation system using Python, Selenium, and third-party OCR providers (Azure OCR); reduced per-application verification time from 10+ minutes to under 1 minute while significantly reducing human error in document classification and data extraction.}
        \resumeItem{Architected and deployed RESTful identity verification service using FastAPI, integrating facial recognition and bank statement analysis APIs; achieved 60\% reduction in manual processing time and improved verification accuracy for financial services clients.}
        \resumeItem{Engineered automated data pipelines integrating web scraping, OCR, and rule-based validation to streamline document processing workflows, handling 100+ daily verification requests for financial data analysis.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Key Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Build Your Own Redis (BYOR)} $|$ \href{https://github.com/premgowda98/byor}{\underline{github.com/premgowda98/byor}}}{2024}
          \resumeItemListStart
            \resumeItem{Implemented production-grade Redis clone in Golang supporting master-slave replication, RDB/AOF persistence, and 8+ data structures (strings, lists, sets, sorted sets, hashes); achieved high feature parity with Redis core functionality.}
            \resumeItem{Designed custom RESP (Redis Serialization Protocol) parser and command execution engine, handling concurrent client connections with goroutines and achieving sub-millisecond latency for GET/SET operations.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{AI-Powered Logistics Automation Platform}}{2025}
          \resumeItemListStart
            \resumeItem{Developed WhatsApp-based logistics automation system for construction materials using Python and Gemini AI to parse bill images and generate structured monthly invoices, reducing manual data entry by 90\%.}
            \resumeItem{Designed high-availability architecture using Amazon SQS for message buffering and RabbitMQ for task distribution to on-premise Kubernetes cluster with MetalLB load balancing, ensuring 99.9\% uptime.}
            \resumeItem{Implemented end-to-end observability using OpenTelemetry, Prometheus, and Grafana for distributed tracing and performance monitoring across microservices.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Personal AI Assistant -- Finance \& Inbox Automation}}{2025}
          \resumeItemListStart
            \resumeItem{Built automation platform using n8n and Telegram bot interface; automated financial data pipelines loading into PostgreSQL for real-time analytics, and implemented LLM-based Gmail classification for automatic newsletter categorization and knowledge base management.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Global Academy of Technology, Bengaluru}{2015 -- 2019}
      {Bachelor of Engineering -- Mechanical Engineering}{CGPA: 8.3/10}
      \resumeItemListStart
        \resumeItem{Self-taught programming through online courses and bootcamps (Python, Data Structures, Algorithms, Web Development) during final year; completed multiple full-stack projects leading to successful career transition into software engineering.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications \& Training}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{RabbitMQ Essentials} (2023) -- Message queuing, high-availability clustering, and broker configuration \\
     \textbf{Redis University (RU101)} (2024) -- Data structures, performance optimization, and data modeling patterns
    }}
 \end{itemize}

\end{document}

